\section{Mathematical Model}
Based on data volume rates, we do need mathematical models to identify which are the source addresses that may be proponents of an attack. Since we categorise data, using big data framework in order to analyse log files and generate, for simplicity we explain each field by referring to a single entry which represents an exchange between a source ip and server.

\begin{itemize}
	\item \textit{n\_packets} \\ Represents the amount of packets.
	\item \textit{total\_volume} \\ It is the sum of all packets length.
	\item \textit{time\_difference} \\ It is the time difference between the first communication and the last one, we consider it as a time window.
	\item \textit{ratio\_vol\_td} \\ Represents the volume over seconds exchanged during the time window.
\end{itemize}

The mathematical model must be able judge the data \cite{detection_by_path_analaysis} by using a threshold, in our case the maximal volume of traffic per second supported by the server under analysis represents this threshold.
This threshold can be estimated by adding an $\alpha$ factor to the mean of volume exchanged during the time of records.

Using \textit{python} in order to manipulate the results returned by \textit{Pig-latin} we decide to use \textbf{standard deviation} as mathematical model to identify suspicious source address.
The formula for the sample standard deviation is

\begin{equation}
\label{eq:standard_dev}
	s = \sqrt{\frac{1}{N-1}\sum_{i=1}^N(x_i - \bar{x})^2}
\end{equation}
where $x_1, x_2\ ...\ x_n$ are the \textit{ratio\_vol\_td} values grouped by source and destination ip, 
\begin{equation}
	\bar{x}= \sum_{i=1}^N \frac{ratio\_vol\_td_i}{n\_packets_i}
\end{equation}
is the mean volume exchanged and $N$ is the number of sample in the dataset generated by \textit{Pig-latin} script. 

We decided to plot as output of analysis the mean value with the difference from mean of each source address which has connected to the server.
